Four reasons your build is slow

### 2019-01-17 paper.tex
change math to equation
figures.

\documentclass[sigconf,10pt,review,authorversion]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{geometry}
\geometry{reset, twoside=true, head=13pt,
     paperwidth=8.5in, paperheight=11in,
     includeheadfoot, columnsep=2pc,
     top=57pt, bottom=73pt, inner=72pt, outer=72pt,
     marginparwidth=2pc,heightrounded
     }
\citestyle{acmnumeric}

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc \$(FLAGS)
  ../lib/common/debug.c
  \textrm{\emph{26 more .c files}}
  zstdcli.o fileio.o bench.o
  datagen.o dibio.o -o zstd
\end{Verbatim}
\caption{A long running cc command which was responsible for about 97\% of zstd's span.  It compiled and linked 27 .c files.}
\label{code:cc1}
\end{figure}

If this call is no longer part of the span, the new span is similarly dominated by another single call to cc;
see fig. \ref{code:cc2}.
\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  cc \$(FLAGS)
  common/debug.c
  \textrm{\emph{29 more .c files}}
  -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{Verbatim}
\caption{A long running cc command which was responsible for aproximately 100\% of zstd's span when \ref{code:cc1} was not a membe rof the span.
This command compiled and linked 30 files.}
\label{code:cc2}
\end{figure}
If neither of these calls are members of the build's span, then our tool predicts the span would be
approximately 7.2 seconds rather than 39 seconds, as with the original span, or 37 seconds, as with the second span.
This is about an 80\% reduction in the build's span, and the parallelism improves from 2.98 to 16.

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
../lib/common/debug.o: ../lib/common/debug.c                                                       
    cc \$(FLAGS) ../lib/common/debug.c
\textrm{\emph{26 more targets; one for each object file}}    
zstd-build: \$(OBJ\_FILES)
    cc \$(FLAGS) \$(OBJ\_FILES) -o zstd
\end{Verbatim}
\caption{Makefile targets which replaced original code in fig. \ref{code:cc1}}
\label{code:cc3}
\end{figure}

@@

\begin{figure}[H]
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
common/debug.o1: common/debug.c
    cc \$(FLAGS) common/debug.c
       -o common/debug.o1
\textrm{\emph{29 more targets; one for each object file}}
libzstd-build: \$(OBJ\_FILES)
    cc \$(FLAGS) \$(OBJ\_FILES) -shared
       -o libzstd.so.1.3.7
\end{Verbatim}
\caption{Makefile targets which replaced original code in fig. \ref{code:cc2}}
\label{code:cc4}
\end{figure}

@@

The following code is an alternative to the code in fig. \ref{code:cc1}. Each file is compiled individually
as its own recipe, followed by a recipe to link the object files together.  This has the same
performance as the original command.
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc \$(FLAGS) ../lib/common/debug.c
   -o ../lib/common/debug.o
\textrm{\emph{26 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -o zstd
\end{Verbatim}

The following code is an alternative to the code in fig. \ref{code:cc2}. Each file is compiled individually
  as its own recipe, followed by a recipe to link the object files together.  This has the same
  performance as the original command.
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
cc \$(FLAGS) common/debug.c -o common/debug.o1
\textrm{\emph{29 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -shared
   -o libzstd.so.1.3.7
\end{Verbatim}

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small,numbers=left,xleftmargin=5mm]
  google/protobuf/descriptor.cc
  google/protobuf/descriptor.pb.cc
  google/protobuf/compiler/cpp/cpp\_message.cc
\end{Verbatim}
\caption{The compilation of these 3 files dominate the longest 3 spans.}
\label{code:g++1}
\end{figure}

>>>>

\documentclass[sigconf,10pt,authorversion]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{geometry}
\geometry{reset, twoside=true, head=13pt,
     paperwidth=8.5in, paperheight=11in,
     includeheadfoot, columnsep=2pc,
     top=57pt, bottom=73pt, inner=72pt, outer=72pt,
     marginparwidth=2pc,heightrounded
     }
\citestyle{acmnumeric}

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
  cc \$(FLAGS) common/debug.c \textrm{\emph{26 more .c files}}
    zstdcli.o fileio.o bench.o datagen.o dibio.o
    -o zstd
\end{Verbatim}
\caption{A long running cc command which was responsible for about 97\% of zstd's span.  It compiled and linked 27 .c files.}
\label{code:cc1}
\end{figure}

If this call is no longer part of the span, the new span is similarly dominated by another single call to cc;
see fig. \ref{code:cc2}.
\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
  cc \$(FLAGS) common/debug.c \textrm{\emph{29 more .c files}}
    -o libzstd.so.1.3.7
\end{Verbatim}
\caption{A long running cc command which was responsible for aproximately 100\% of zstd's span when the command in fig. \ref{code:cc1} is removed.
This command compiled and linked 30 files.}
\label{code:cc2}
\end{figure}
If neither of these calls are members of the build's span, then our tool predicts the span would be
approximately 7.2 seconds rather than 39 seconds, as with the original span, or 37 seconds, as with the second span.
This is about an 80\% reduction in the build's span, and the parallelism improves from 2.98 to 16.

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
common/debug.o: common/debug.c                                                       
    cc \$(FLAGS) common/debug.c
\textrm{\emph{26 more targets; one for each object file}}    
zstd-build: \$(OBJ\_FILES)
    cc \$(FLAGS) \$(OBJ\_FILES) -o zstd
\end{Verbatim}
\caption{Makefile targets which replaced original code in fig. \ref{code:cc1}}
\label{code:cc3}
\end{figure}

@@

\begin{figure}[H]
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
common/debug.o1: common/debug.c
    cc \$(FLAGS) common/debug.c
       -o common/debug.o1
\textrm{\emph{29 more targets; one for each object file}}
libzstd-build: \$(OBJ\_FILES)
    cc \$(FLAGS) \$(OBJ\_FILES) -shared
       -o libzstd.so.1.3.7
\end{Verbatim}
\caption{Makefile targets which replaced original code in fig. \ref{code:cc2}}
\label{code:cc4}
\end{figure}

@@

The following code is an alternative to the code in fig. \ref{code:cc1}. Each file is compiled individually
as its own recipe, followed by a recipe to link the object files together.  This has the same
performance as the original command.
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
cc \$(FLAGS) common/debug.c
   -o common/debug.o
\textrm{\emph{26 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -o zstd
\end{Verbatim}

The following code is an alternative to the code in fig. \ref{code:cc2}. Each file is compiled individually
  as its own recipe, followed by a recipe to link the object files together.  This has the same
  performance as the original command.
  \begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
cc \$(FLAGS) common/debug.c -o common/debug.o1
\textrm{\emph{29 more recipes; one for each .c file that needs to be compiled}}
cc \$(FLAGS) \$(OBJ\_FILES) -shared
   -o libzstd.so.1.3.7
\end{Verbatim}

@@

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
  google/protobuf/descriptor.cc
  google/protobuf/descriptor.pb.cc
  google/protobuf/compiler/cpp/cpp\_message.cc
\end{Verbatim}
\caption{The compilation of these 3 files dominate the longest 3 spans.}
\label{code:g++1}
\end{figure}
